Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-10-24 cbm-rbd-paper.tex
RBD figure, surv sign table

\section{***Adaptive system RUL / RLD based on Weibull component models}

@@

To calculate the current system reliability function $\Rsysnow(t)$,
we thus need, for each $k=1,\ldots, K$, the probabilities $P(C^k_t = l_k)$
for the number of type $k$ components that function at times $t > \tnow$.
In the Bayesian framework, these probabilities are given
by a so-called posterior predictive distribution that can be derived from the posterior over $\lambda$.

@@

>>>>

\section{Adaptive system residual life distribution based on Weibull component models}

@@

To calculate the current system reliability function $\Rsysnow(t)$,
we thus need, for each $k=1,\ldots, K$, the probabilities $P(C^k_t = l_k)$
for the number of type $k$ components that function at times $t > \tnow$,
taking into account all information available at $\tnow$.
In the Bayesian framework, these probabilities are given
by a so-called posterior predictive distribution that can be derived from the posterior over $\lambda$.

@@

Note that through the condition $T^k > \tnow$, we also take into account
that the components in the system age $\tnow$.
